% !TEX root = ../thesis.tex

\chapter*{Abstract}

Puzzle games have successfully been designed entirely by hand or completely through computer generation. Can value be derived from combining both strategies towards puzzle design and, if so, in what way?

To address this question, we developed MixedAim, a tool with which designers can interactively co-create Sokoban-like puzzles through direct manipulation and steering passively presented level suggestions. 
We conducted a think-aloud user study followed by a structured interview with experts on the subject, identified conventional design approaches, and analyzed in which ways interactions with MixedAim supported these approaches.
Furthermore, we analyzed how our participants adapted to the MixedAim suggestions, identified that the perceived usefulness is dependent on the role of MixedAim in the design process and noticed that it was particularly good at identifying interesting mechanics in small levels with many possible variations.

In conclusion, we found that MixedAim benefitted puzzle designers as another tool in their toolset for creating puzzle games but received concerns that the tool can make it easy to create complicated and bad levels which adds to the responsibility of the designers planning to incorporate MixedAim in their workflow.


\cleardoublepage
\chapter*{Acknowledgement}

I want to thank my supervisor Dr. Anna Feit for her continued support during the weekly interviews, for her input concerning the preparations and execution of the user study, for frequently sending me papers on the topic and giving me feedback on the wording and structure of the thesis. I would also like to thank Prof. Dr. Otmar Hilliges for enabling this passion-driven BSc. thesis.   
Lastly, I would like to thank all participants for taking their time and providing valuable insights without which this thesis would never have been possible.
